Context-dependent consequences of including lagged effects in demographic models

### 2022-05-24 docs/paper.Rmd
run to get working

<!--# probably can't make the figure with the table in it in R easily. -->\
\
Just playing with something here.
This is the population trajectories from the iterated IPMs with `normalize_pop_size=FALSE`.
I thought maybe I'd be able to see some (lagged) similarities between the kernel sampled and DLNM IPMs because they are run with the same sequence of years.
Nothing obvious pops out.
Not sure this figure is worth including.

```{r}
#| pva,
#| fig.cap = "Population trajectories for all three IPMs in both habitats"
tar_load(c(
  ipm_det_cf,
  ipm_det_ff,
  ipm_stoch_cf,
  ipm_stoch_ff,
  ipm_dlnm_cf,
  ipm_dlnm_ff
))

>>>>

<!--# probably can't make the figure with the table in it in R easily. -->

\
\
Just playing with something here.
This is the population trajectories from the iterated IPMs with `normalize_pop_size=FALSE`.
I thought maybe I'd be able to see some (lagged) similarities between the kernel sampled and DLNM IPMs because they are run with the same sequence of years.
Nothing obvious pops out.
Not sure this figure is worth including.

```{r eval=FALSE}
#| pva,
#| fig.cap = "Population trajectories for all three IPMs in both habitats"
tar_load(c(
  ipm_det_cf,
  ipm_det_ff,
  ipm_stoch_cf,
  ipm_stoch_ff,
  ipm_dlnm_cf,
  ipm_dlnm_ff
))
